|

### 2019-03-18 Paper.Rmd
analysis

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'H')
library(tigris)
library(gplots)
library(foreign)
library(car)
library(qwraps2)
library(knitr)
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'H')
library(tigris)
library(gplots)
library(foreign)
library(car)
library(qwraps2)
library(knitr)
library(ggplot2)
library(plotrix)
library(stargazer)
library(doBy)
```

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}

# Read in mean and median data, merge files
total_clean_mean_drop_zeros <- read.csv("../total_clean_mean_drop_zeros.csv")
total_clean_median_drop_zeros <- read.csv("../total_clean_median_drop_zeros.csv")
total_clean_median_drop_zeros$dist_100_mean <- total_clean_mean_drop_zeros$dist_100_mean
total_clean_median_drop_zeros$dist_200_mean <- total_clean_mean_drop_zeros$dist_200_mean
total_clean_median_drop_zeros$dist_300_mean <- total_clean_mean_drop_zeros$dist_300_mean

final.data <- total_clean_median_drop_zeros

# Fill in missing row
final.data[final.data$X==45646,]$dist_100_mean <- total_clean_mean_drop_zeros[total_clean_mean_drop_zeros$X==45646,]$merged_2014_100_mean
final.data[final.data$X==45646,]$dist_200_mean <- total_clean_mean_drop_zeros[total_clean_mean_drop_zeros$X==45646,]$merged_2014_200_mean
final.data[final.data$X==45646,]$dist_300_mean <- total_clean_mean_drop_zeros[total_clean_mean_drop_zeros$X==45646,]$merged_2014_300_mean
final.data[final.data$X==45646,]$dist_100_median <- final.data[final.data$X==45646,]$merged_2014_100_median
final.data[final.data$X==45646,]$dist_200_median <- final.data[final.data$X==45646,]$merged_2014_200_median
final.data[final.data$X==45646,]$dist_300_median <- final.data[final.data$X==45646,]$merged_2014_300_median

# Encode time and treatment dummies
final.data$time <- ifelse(final.data$year_index >= 1, 1, 0)
final.data$treated <- ifelse(final.data$simple415 == "On-site BMR Project", 1, 0)
final.data$did = final.data$time * final.data$treated

no.outliers <- final.data[final.data$LocationKey != "(37.79054, -122.3959)",]
```

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, results='asis'}

m1 <- lm(log(dist_100_median) ~ treated + time + did, data = final.data)
m2 <- lm(log(dist_200_median) ~ treated + time + did, data = final.data)
m3 <- lm(log(dist_300_median) ~ treated + time + did, data = final.data)

m4 <- lm(log(dist_100_mean) ~ treated + time + did, data = final.data)
m5 <- lm(log(dist_200_mean) ~ treated + time + did, data = final.data)
m6 <- lm(log(dist_300_mean) ~ treated + time + did, data = final.data)

stargazer(m1, m2, m3, type='latex', 
          dep.var.labels=c("Log(100m Median)","Log(200m Median)", "Log(300m Median)"),
          covariate.labels=c("On-Site Affordable Housing", "Post-Treatment", "Diff-in-Diff Estimator", "Constant"),
          font.size="small", header=FALSE)

stargazer(m4, m5, m6, type='latex', 
          dep.var.labels=c("Log(100m Mean)","Log(200m Mean)", "Log(300m Mean)"),
          covariate.labels=c("On-Site Affordable Housing", "Post-Treatment", "Diff-in-Diff Estimator", "Constant"),
          font.size="small", header=FALSE)

```

```{r}

# Visualize diff in diff model

year_means <- summaryBy(dist_300_median ~ treated + year_index, data=final.data, FUN=c(length,median,sd))
ggplot(data=year_means, aes(x=year_index,y=dist_300_median.median)) + geom_point() + 
    geom_line(data = year_means[year_means$treated==1,], aes(x = year_index, y = dist_300_median.median), color = "blue") +
  geom_line(data = year_means[year_means$treated==0,], aes(x = year_index, y = dist_300_median.median), color = "red") + xlim(-2,2) + geom_vline(xintercept=0)

```

- Run separate regressions: subset data to only t-1, t+1, etc.
